Canonical rings of $\bq$-divisors on Minimal Rational Surfaces

### 2015-07-30 surfaces-write-up/surface-write-up.tex
fixed some todos

\begin{rem}
\label{rem:ghost-motivation}
Example ~\ref{eg:hyperplane} shows that the naive generalization of
~\cite[Theorem 8]{dorney:canonical} of generation in degree at most
$\sum_{i=1}^{n}\ell_i$ cannot possibly hold. The reason for this is
that the divisors may ``be contained in a hyperplane,'' i.e.~ be
expressible as functions in $m$ of the $m+1$ variables on $\bp^m$.
This problem can easily be circumvented by adding in ``ghost
points.'' That is, we may add divisors of the form $0 \cdot H_i$ to
$D$, and reorder so that if $D = \sum_{i=1}^{n}\alpha_i V(f_i)$,
then $f_0, \ldots, f_n$.

@@

\end{lem}
\begin{proof}
Let 
\begin{align}\label{eqn:Sigma-def}
	\Sigma = \left \{(d, c_1, \ldots, c_n) \in \bz^{n+1} : c_i \geq - d
\alpha_i, \; 1 \leq i \leq n, \text{ and } \sum_{i=1}^{n} \ell_i \bida_i = 0
\right \}.
\end{align}
\todo{Aaron: Possibly take this definition out of the proof, and move it into the setup, since we want to reference it later.}
We note that $\Sigma$ has extremal rays given by the lattice points 
\begin{equation}\label{defn:e-i-proj}
	e_i = \left(\ell_i \bida_i, - \alpha_1 \ell_i \bida_i, \ldots
-\alpha_{i-1} \ell_i \bida_i, \ell_i \sum_{j\ne i} \alpha_j \bida_j,
-\alpha_{i+1} \ell_i \bida_i, \ldots, -\alpha_n, \ell_i \bida_i \right)
\end{equation}
for each $i\in \{1, \ldots n\}$.
Therefore, applying Proposition ~\ref{prop:cone-generation}, we see $R_D$ is generated in degrees less than
\[
	\sum_{i=1}^n \ell_i a_i.
\]
\end{proof}

@@

\todo{say something about ghost points?}

@@

For the remainder of this section we will assume $D_1, D_2, D_3,$ and $D_4$ are
distinct divisors with bi-degrees $(1,0)$
, $(1,0)$, $(0,1)$, and $(0,1)$ respectively. Let $D_i = V(f_i)$ where
$f_i \in \sco(\bida_i, \bidb_i)$.  
Then, $f_1$ and $f_2$ are independent linear
polynomials in $x_0$ and $x_1$ and $f_3$ and $f_4$ are independent
linear polynomials in $y_0$ and $y_1$.
\begin{defn}
Define 
\begin{equation}
\label{eqn:define-T=(D)}
	\Te(D) = \left\{i \in \{1, \ldots, n\}: \bida_i \sum_{k=1}^n \bidb_k 
\alpha_k = \bidb_i \sum_{k=1}^n \bida_k \alpha_k \right\},
\end{equation}

@@

\[
	e_i := (1, -\alpha_1, \ldots, -\alpha_{i-1}, \frac{\sum_{j \ne i}
	\alpha_j (\bida_j + \bidb_j)}{\bida_i + \bidb_i}, -\alpha_{i + 1},
	\ldots, -\alpha_n).
\]
for $1 \leq i \leq n$.

Let $\Sigma_1 \otimes_\bz \bq$ be the $\bq_{\ge 0}$ span of $e_1, \ldots e_n$.
We can intersect $\Sigma_1 \otimes_\bz \bq$ with the hyperplane $H :=
V(\sum_{i=1}^n \bida_i X_i)$  to get the subspace $\Sigma \otimes_\bz \bq = H \cap \Sigma_1
\otimes_\bz \bq$.  Then, the extremal rays of $\Sigma$ are precisely the extremal 
rays of $\Sigma \otimes_\bz \bq$.

@@

The following are elements of $R_D$ correspond to the extremal rays of
$\Sigma$.
\todo{Aaron: can we rephrase the above to say the images of the $\epsilon_i, \epsilon_{ij}$ lie on the extremal rays?}
For $i \in \Te(D)$, define $\epsilon_i \in R_D$ in degree $d_i = \ell_i \gcd(a_i, b_i)$ by 
\todo{below section needs to be simplified, maybe
by introducing new variables; 
Peter: I replaced some terms with degrees $d_i$ and $d_{i,j}$}
\begin{equation}\label{eqn:epsilon_i}
	\epsilon_i := \left(\prod_{k \ne i} f_k^{-\alpha_k d_i}\right)
	f_i^{ \frac{d_i}{\bida_i + \bidb_i}\sum_{k \ne i}
	\alpha_k (\bida_k + \bidb_k)}.
\end{equation}

\noindent
For $i \in \Tp(D)$ and $j \in \Tm(D)$, define $\epsilon_{i,j}\in R_D$ in degree $d_{i,j} = \ell_{i, j}(\bida_i \bidb_j - \bida_j \bidb_i)$ by
\begin{equation}\label{eqn:epsilon_i,j}
	\epsilon_{i, j} := \left(\prod_{k \ne i, j} f_k^{-\alpha_k d_{i,j}} \right){f_i}^{s_1} {f_j}^{s_2}
\end{equation}

\noindent
where
\[
	s_1 = \bidb_j \sum_{k \ne i,j} \alpha_k \bida_k - \bida_j \sum_{k \ne i, j}
	\alpha_k \bidb_k
\]

\noindent
and
\[
	s_2 = -\bidb_i \sum_{k \ne i, j} \alpha_k \bida_k + \bida_i \sum_{k \ne i, j}
	\alpha_k \bidb_k.
\]
\todo{Aaron: Why are $\epsilon_{i,j}$ defined here instead of $e_{i,j}$. We
don't use the $\epsilon$ here, and we do use the $e$ here. \\
Peter: I have a slight leaning towards this notation, because the algebraic
object is use more later (I think, although I'll check to make sure); also, I
think writing out the ordered tuple would actually be harder, because there is
no product notation, and it can be hard to denote the cordinates.

Aaron: I did
a search for $\epsilon$ and the last time it is mentioned is inside this proof.
In fact, while the $\epsilon$ are not referred to later, the $e_{ij}$ are referred to!
The ordered tuple will look slightly longer, but it is less confusing then
switching from tuple notation to
product notation for no reason, especially when it isn't used again.
It's confusing for the reader who is thinking in terms of lattice points
to suddently switch to thinking in a ring. At the very least, you should say 
it is the preimage of the map from the lattice to the canonical ring, since the
current use of corresponding isn't ever made clear, but
this would probably then take a bunch more space too, and I would also find this significantly more confusing than just saying the lattice points.

Robin: Yeah, I thought that we had agreed upon doing the entire
proof in terms of the lattice points and then occasionally giving
the algebraic translation (and noting that it is simply the
algebraic translation) rather than this ``in-between'' sort of
thing. I agree with Aaron that it's confusing for a reader who has
not gone through the details before.}

A quick calculation deduces that these $\epsilon_i$'s and
$\epsilon_{i,j}$'s lie on the extremal rays represented by the
$e_i$'s and $e_{i,j}$'s, respectively.
\begin{rem}
For the remainder of this section replace the $e_i$'s and $e_{i,j}$'s with a (possibly) different representative of it's extremal ray say that their lattice points correspond to the $\epsilon_i$'s and $\epsilon_{i,j}$'s, respectively.
\end{rem}

\todo{Peter: I don't like having a remark inside of a proof.  Also, it feels
like this could reasonably be replaced with a better constructed/organized
proof, so that $e_i$'s are just defined this way initially; let me know if you
see a good way to do so...  As for Aaron's comment above, we could do something
like that, except we already defined $e_i$'s to be something different, which
might be equally/more confusing.
Aaron: I also don't like this here, just because it isn't really a remark,
its more of a notational convention, and it doesn't really belong in the proof.
I also think it's confusing to switch notation in the middle of a proof.
Earlier in the proof, we should just call the $e_{ij}$ something like $\hat{e_{ij}}$. Then, we should never define $\epsilon_{ij}$, since it's only used in this
proof, and should really be $e_{ij}$, as I was explaining in my previous todo.
Instead of defining $\epsilon_{ij}$, just define $e_{ij}$ which are the
appropriately scaled $\hat{e_{ij}}$ and everything will be much clearer.
Robin: agree with Aaron here.}

@@

Let $\omega\in \Omega'$ correspond to the monomial $y_i \prod_{j=1}^n
{y_j}^{c_j}$.  Then we can write $\omega$ as a sum of $r_j e_j$'s for $j\in
\Te$ and $r_{j,k}e_{j,k}$ for $j\in \Tp, k\in \Tm$.  
For convenience, let $e_j$ (when it exists) be in degree $d_j$ with $j^{th}$
component $-\alpha_j d_j + \kappa_j$ for some $\kappa_j \in \bq$ and let $e_{j,k}$ (when it exists) lie in
degrees $d_{j,k}$ with $j^{th}$ component $-\alpha_j d_{j,k} + \kappa_{j,k}'$ and $k^{th}$
component $-\alpha_j d_{j,k} + \kappa_{j,k}''$ for $\kappa_{j,k}', \kappa_{j,k}'' \in \bq$
By a careful computation, we can find $\lambda \in \Sigma$ 
\todo{Aaron: Is it at all possible to write down what $\lambda$ and the $r_{i,j}$ are?
I suspect we should be able to write them in a couple lines, which would
definitely clarify how we're getting the bound on degree $E$. While I agree
it's fine to hide the computation of the $r_{i,j}$ it would still clarify matters
to say what the $r_{i,j}$ and $\lambda$ are.}
and $r_{i,j} \in \bq$ so that we can write
\begin{equation}\label{eqn:sigma-in-terms-of-lambda/E}
-	\sigma = \lambda + E
 \end{equation}
with $E$ of the form
\begin{equation}\label{eqn:hirz-E-translation}
	E = \begin{cases}
	\frac{1}{\kappa_i} e_i  	&  \mbox{ if }i\in \Te\\
	\sum_{j\in \Tm} r_{i,j} e_{i,j}: r_{i,j}\in \bq, \sum_{j\in \Tm} r_{i,j}\kappa_{i,j}' = 1 & \mbox{ if } i\in \Tp\\
	\sum_{j\in \Tp} r_{j,i} e_{j,i}: r_{j,i} \in \bq, \sum_{j\in \Tm} r_{j,i} \kappa_{i,j}'' = 1 	& \mbox{ if } i\in \Tm\\
	\end{cases}.
\end{equation}

@@

However, I'm really baffled as to why you want to apply $\psi$ to the
$\beta_i$, since two lines later, you then apply the reverse correspondence
and want to work back in the semigroupring. Why don't you just stay in the
semigroup ring the whole time?
I think I'm misunderstanding this, but is $\omega_\mu$ just equal to
$\beta_i$ for some $i$? Also, why is $\omega_\mu$ missing a $d$ index
as its first index?
}
\todo{Aaron: Again, why do we keep defining lattce points in
	terms of elements in the canonical ring? Why not just
write out what the lattice points are in coordinates? \\ 
Peter: Fixed?

Aaron: I like that $E$ is defined in terms of $e_i$.
I'm still confused about $\omega$ and $\mu$ though. see my above comment.
}
can further compute that there exist $q_i, q_{i,j} \in \bq_{\geq 0}$ and $\lambda \in
\Sigma$ so that the lattice point, $\omega_\mu = (c_1 ,\ldots c_n)$,
corresponding to $\mu
$ is of the form
\[
	\omega_\mu = \lambda + E_\mu
\]
where $\lambda$ is the same as in Equation \ref{eqn:sigma-in-terms-of-lambda/E} and $E_\mu$ is defined in a similar fashion as $E$ in Equation \ref{eqn:hirz-E-translation} by
\begin{equation}\label{eqn:hirz-E_mu-translation}
E_\mu = \left(\sum_{\substack{i \in \{1, 2, 3, 4\} \cap \Te}}q_i e_i\right) +
\left(\sum_{\substack{i \in \{1, 2, 3, 4\} \cap \Tp \\ j\in \Tm}} q_{i,j}
e_{i,j}\right) + \left(\sum_{\substack{i \in \{1, 2, 3, 4\} \cap \Tm \\ j\in
\Tp}} q_{j,i} e_{i,j}\right).
\end{equation}
\todo{Aaron: if $\sigma_\mu$ is an element, how can it be written as
	the sum of an element and a set? Same question for $\sigma$ above.
	Also, I do not know what $E_\mu$ is. You really have to define it,
since there's no way to check the validity of this proof without it.  \\
Peter: $E$ and $E_\mu$ are elements, not sets...

Aaron: My mistake. Thanks for writing it out though. However,
since $E, E_\mu$ are so similar, why not defining them so that they look similar?
I.e., why not define them either both in three cases as $E$
or both as sums as $E_\mu$. It's confusing that they are the same, but not
written in a parallel fashion.
}
Note that $E_\mu$ lies in the same degree as $E$ for all $\mu$.

@@

\todo{add something about ghost points?}

>>>>

\begin{rem}\todo{Peter: maybe move this out of a remark and just say it with the previous example?  As it stands, the previous example is a little unclear as to what its purpose is...}
\label{rem:ghost-motivation}
Example ~\ref{eg:hyperplane} shows that the naive generalization of
~\cite[Theorem 8]{dorney:canonical} of generation in degree at most
$\sum_{i=1}^{n}\ell_i$ cannot possibly hold. The reason for this is
that the divisors may ``be contained in a hyperplane,'' i.e.~ be
expressible as functions in $m$ of the $m+1$ variables on $\bp^m$.
This problem can easily be circumvented by adding in ``ghost
points.'' That is, we may add divisors of the form $0 \cdot H_i$ to
$D$, and reorder so that if $D = \sum_{i=1}^{n}\alpha_i V(f_i)$,
then $\bk[f_0, \ldots, f_m]$ has transcendence degree $m+1$ over $\bk$.

@@

\end{lem}
\begin{proof}
Let 
\begin{align}\label{eqn:Sigma-def}
	\Sigma = \left \{(d, c_1, \ldots, c_n) \in \bz^{n+1} : c_i \geq - d
\alpha_i, \; 1 \leq i \leq n, \text{ and } \sum_{i=1}^{n} \ell_i \bida_i = 0
\right \}.
\end{align}
\todo{Aaron: Possibly take this definition out of the proof, and move it into the setup, since we want to reference it later.  \\
Peter: I like having the statement of the lemma being nice and consise; also the statement has nothing to do with this geometric picture, so I find it more natural to have the geometric side contained in the proof.  I also don't quite see why it is so bad to reference something from inside a previous proof; a reader can surely locate it...
}
We note that $\Sigma$ has extremal rays given by the lattice points 
\begin{equation}\label{defn:e-i-proj}
	e_i = \left(\ell_i \bida_i, - \alpha_1 \ell_i \bida_i, \ldots
-\alpha_{i-1} \ell_i \bida_i, \ell_i \sum_{j\ne i} \alpha_j \bida_j,
-\alpha_{i+1} \ell_i \bida_i, \ldots, -\alpha_n, \ell_i \bida_i \right)
\end{equation}
for each $i\in \{1, \ldots n\}$.
Therefore, applying Proposition ~\ref{prop:cone-generation}, we see $R_D$ is generated in degrees less than
\[
	\sum_{i=1}^n \ell_i a_i.
\]
\end{proof}

@@

\todo{say something about ghost points? Peter: Haven't we already done that at the begining of the section?}

@@

For the remainder of this section we will assume $D_1, D_2, D_3,$ and $D_4$ are
distinct divisors with bi-degrees $(1,0)$
, $(1,0)$, $(0,1)$, and $(0,1)$ respectively. Let $D_i = V(f_i)$ where
$f_i \in \sco(\bida_i, \bidb_i)$.  
Then, $f_1$ and $f_2$ are independent linear
polynomials in $x_0$ and $x_1$ and $f_3$ and $f_4$ are independent
linear polynomials in $y_0$ and $y_1$.  In order to achieve this condition on $D_1, \ldots D_4$, it may be necessary to add in ``Ghost Divisors'' (i.e. divisors with of the desired form with a coefficient $\alpha_i = 0$).
\begin{defn}
Define 
\begin{equation}
\label{eqn:define-T=(D)}
	\Te(D) = \left\{i \in \{1, \ldots, n\}: \bida_i \sum_{k=1}^n \bidb_k 
\alpha_k = \bidb_i \sum_{k=1}^n \bida_k \alpha_k \right\},
\end{equation}

@@

\[
	\epsilon_i := (1, -\alpha_1, \ldots, -\alpha_{i-1}, \frac{\sum_{j \ne i}
	\alpha_j (\bida_j + \bidb_j)}{\bida_i + \bidb_i}, -\alpha_{i + 1},
	\ldots, -\alpha_n).
\]
for $1 \leq i \leq n$.

Let $\Sigma_1 \otimes_\bz \bq$ be the $\bq_{\ge 0}$ span of $\epsilon_1, \ldots \epsilon_n$.
We can intersect $\Sigma_1 \otimes_\bz \bq$ with the hyperplane $H :=
V(\sum_{i=1}^n \bida_i X_i)$  to get the subspace $\Sigma \otimes_\bz \bq = H \cap \Sigma_1
\otimes_\bz \bq$.  Then, the extremal rays of $\Sigma$ are precisely the extremal 
rays of $\Sigma \otimes_\bz \bq$.

@@

From this we can deduce the representatives of $\Sigma$ lying on its extremal rays given by the following:
For $i \in \Te(D)$, define $e_i \in R_D$ in degree $d_i = \ell_i \gcd(a_i, b_i)$ by 
\begin{equation}\label{eqn:epsilon_i}
	e_i := (-\alpha_1 d_i, \ldots, - \alpha_{i-1} d_i, \frac{d_i}{\bida_i + \bidb_i}\sum_{k \ne i}
	\alpha_k (\bida_k + \bidb_k), - \alpha_{i+1} d_i, \ldots, - \alpha_n d_i)
\end{equation}

\noindent
For $i \in \Tp(D)$ and $j \in \Tm(D)$, define $e_{i,j}\in R_D$ in degree $d_{i,j} = \ell_{i, j}(\bida_i \bidb_j - \bida_j \bidb_i)$ by
\begin{equation}\label{eqn:epsilon_i,j}
	\begin{split}& e_{i,j} := (-\alpha_1 d_{i,j}, \ldots -\alpha_{i-1} d_{i,j}, \bidb_j \sum_{k \ne i,j} \alpha_k \bida_k - \bida_j \sum_{k \ne i, j}
	\alpha_k \bidb_k, -\alpha_{i+1} d_{i,j}, \\
	&\ldots -\alpha_{j-1} d_{i,j}, -\bidb_i \sum_{k \ne i, j} \alpha_k \bida_k + \bida_i \sum_{k \ne i, j}
	\alpha_k \bidb_k, -\alpha_{j+1}d_{i,j}, \ldots, - \alpha_{n}d_{i,j}).
	\end{split}
\end{equation}
Note that the above expression is for when $i < j$, but a small rearangement gives when $j < i$.  \todo{Peter: I changed the above expression, but I'm still feel a little dubious that this is easier to read...}

%\noindent
%where
%\[
%	s_1 = \bidb_j \sum_{k \ne i,j} \alpha_k \bida_k - \bida_j \sum_{k \ne i, j}
%	\alpha_k \bidb_k
%\]
%
%\noindent
%and
%\[
%	s_2 = -\bidb_i \sum_{k \ne i, j} \alpha_k \bida_k + \bida_i \sum_{k \ne i, j}
%	\alpha_k \bidb_k.
%\]

A quick calculation deduces that these $e_i$'s and
$e_i{i,j}$'s lie on the extremal rays of $\Sigma$.
%\begin{rem}
%For the remainder of this section replace the $e_i$'s and $e_{i,j}$'s with a %(possibly) different representative of it's extremal ray say that their lattice points %correspond to the $\epsilon_i$'s and $\epsilon_{i,j}$'s, respectively.
%\end{rem}

%\todo{Peter: I don't like having a remark inside of a proof.  Also, it feels
%like this could reasonably be replaced with a better constructed/organized
%proof, so that $e_i$'s are just defined this way initially; let me know if you
%see a good way to do so...  As for Aaron's comment above, we could do something
%like that, except we already defined $e_i$'s to be something different, which
%might be equally/more confusing.
%Aaron: I also don't like this here, just because it isn't really a remark,
%its more of a notational convention, and it doesn't really belong in the proof.
%I also think it's confusing to switch notation in the middle of a proof.
%Earlier in the proof, we should just call the $e_{ij}$ something like $\hat{e_{ij}}$. Then, we should never define $\epsilon_{ij}$, since it's only used in this
%proof, and should really be $e_{ij}$, as I was explaining in my previous todo.
%Instead of defining $\epsilon_{ij}$, just define $e_{ij}$ which are the
%appropriately scaled $\hat{e_{ij}}$ and everything will be much clearer.
%Robin: agree with Aaron here.}

@@

Let $\omega\in \Omega'$ correspond to the monomial $y_i \prod_{j=1}^n
{y_j}^{c_j}$.  Then we can write $\omega$ as a sum of $r_j e_j$'s for $j\in
\Te$ and $r_{j,k}e_{j,k}$ for $j\in \Tp, k\in \Tm$.  
For convenience, let $e_j$ (when it exists) be in degree $d_j$ with $j^{th}$
component $-\alpha_j d_j + \kappa_j$ for some $\kappa_j \in \bq$ and let $e_{j,k}$ (when it exists) lie in
degrees $d_{j,k}$ with $j^{th}$ component $-\alpha_j d_{j,k} + \kappa_{j,k}'$ and $k^{th}$
component $-\alpha_j d_{j,k} + \kappa_{j,k}''$ for $\kappa_{j,k}', \kappa_{j,k}'' \in \bq$
By a careful computation, we can find $\lambda \in \Sigma$ 
\todo{Aaron: Is it at all possible to write down what $\lambda$ and the $r_{i,j}$ are?
I suspect we should be able to write them in a couple lines, which would
definitely clarify how we're getting the bound on degree $E$. While I agree
it's fine to hide the computation of the $r_{i,j}$ it would still clarify matters
to say what the $r_{i,j}$ and $\lambda$ are.
\\
Peter: There is not a unique choice of the $r_{i,j}$'s.  When we write out $\sigma$ in terms of the $e_i$'s and $e_{i,j}'s$ with coefficients $C_i$ and $C_{i,j}$, any choice of $r_{i,j}$'s that are at most equal to the coefficient $C_{i,j}$ and such that $\sum_{j\in T_-} r_{i,j}\kappa'_{i,j}=1$ will work.}
and $r_{i,j} \in \bq$ (in general such a choice may be very non-unique) so that we can write
\begin{equation}\label{eqn:sigma-in-terms-of-lambda/E}
	\sigma = \lambda + E
 \end{equation}
with $E$ of the form
\begin{equation}\label{eqn:hirz-E-translation}
	E = \begin{cases}
	\frac{1}{\kappa_i} e_i  	&  \mbox{ if }i\in \Te\\
	\sum_{j\in \Tm} r_{i,j} e_{i,j}: r_{i,j}\in \bq, \sum_{j\in \Tm} r_{i,j}\kappa_{i,j}' = 1 & \mbox{ if } i\in \Tp\\
	\sum_{j\in \Tp} r_{j,i} e_{j,i}: r_{j,i} \in \bq, \sum_{j\in \Tm} r_{j,i} \kappa_{i,j}'' = 1 	& \mbox{ if } i\in \Tm\\
	\end{cases}.
\end{equation}

@@

However, I'm really baffled as to why you want to apply $\psi$ to the
$\beta_i$, since two lines later, you then apply the reverse correspondence
and want to work back in the semigroupring. Why don't you just stay in the
semigroup ring the whole time?
I think I'm misunderstanding this, but is $\omega_\mu$ just equal to
$\beta_i$ for some $i$? Also, why is $\omega_\mu$ missing a $d$ index
as its first index?
\\
Peter: $\beta_i$'s are polynomials in $f_1, \ldots f_4$.  By the monomial terms in $\beta_i$ I mean look at each monomial appearing in this polynomial and take the set of those.
}
can further compute that there exist $q_i, q_{i,j} \in \bq_{\geq 0}$ and $\lambda \in
\Sigma$ so that the lattice point, $\omega_\mu = (c_1 ,\ldots c_n)$,
corresponding to $\mu
$ is of the form
\[
	\omega_\mu = \lambda + E_\mu
\]
where $\lambda$ is the same as in Equation \ref{eqn:sigma-in-terms-of-lambda/E} and $E_\mu$ is defined in a similar fashion as $E$ in Equation \ref{eqn:hirz-E-translation} by
\begin{equation}\label{eqn:hirz-E_mu-translation}
E_\mu = \left(\sum_{\substack{i \in \{1, 2, 3, 4\} \cap \Te}}q_i e_i\right) +
\left(\sum_{\substack{i \in \{1, 2, 3, 4\} \cap \Tp \\ j\in \Tm}} q_{i,j}
e_{i,j}\right) + \left(\sum_{\substack{i \in \{1, 2, 3, 4\} \cap \Tm \\ j\in
\Tp}} q_{j,i} e_{i,j}\right).
\end{equation}
\todo{Aaron: if $\sigma_\mu$ is an element, how can it be written as
	the sum of an element and a set? Same question for $\sigma$ above.
	Also, I do not know what $E_\mu$ is. You really have to define it,
since there's no way to check the validity of this proof without it.  \\
Peter: $E$ and $E_\mu$ are elements, not sets...

Aaron: My mistake. Thanks for writing it out though. However,
since $E, E_\mu$ are so similar, why not defining them so that they look similar?
I.e., why not define them either both in three cases as $E$
or both as sums as $E_\mu$. It's confusing that they are the same, but not
written in a parallel fashion.
\\
Peter: Well... We had a conversation a while ago that saying something like $j \in \{i\} \cap T_=$ might look a little funny (saying $j$ ranging over the set of i intersect $T_=$ meaning $j$ either ranges over the emptyset or the singleton set of $i$).  I We could make this change in the first one if it is preferable.  On the other hand, transforming the second into the form of the first would be terribly ugly (like 12 cases, some of which are sumed together... or something like that...).
}
Note that $E_\mu$ lies in the same degree as $E$ for all $\mu$.

@@
